On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-07-26 Manuscript/manuscript.tex
Added table back

%\begin{table}
  %\centering
  %\caption{Compares the various effect models by dataset, all probabilities are
  %for observing a reaction time less than 0.1 seconds. In general the model with
  %the highest probability (least extreme reaction time) is the Year Effect model.}
  %\begin{tabular}{c c c c} 
  % \toprule
  % Data Set & Year Effect & Batch Effect & Both Effects \\ 
   %\midrule
   %Old Pooled & $5.73\cdot10^{-3}$ & $5.21\cdot10^{-3}$ & $4.15\cdot10^{-3}$ \\ 
   %All Pooled & $6.84\cdot10^{-3}$ & $6.64\cdot10^{-3}$ & $5.15\cdot10^{-3}$ \\
   %\bottomrule
  %\end{tabular}
  %\label{tab:EffectComparison}
%\end{table}

@@

\begin{table}
  \centering
  \caption{}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & $exact = True$ & $exact \neq True$ & Sample size & Clusters/Athletes \\ 
   \midrule
   2019 vs 2022 & $2.9\cdot10^{-3}$ & $2.3\cdot10{-2}$ & 65 & 15 \\ 
   International & $2.2\cdot10^{-16}$ & $3.1\cdot10^{-4}$ & 61 & 15 \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}
The p value from the two group comparison for 2019 and 2022 was 0.001464.  This 
value is for a one-sided test and show that the mean reaction time on average in
2019 was larger (slower) than the mean reaction time in 2022 for athletes who 
competed in both championships at an $\alpha$ level of 0.01. This provides good
evidence that on average, the reaction times from the 2019 and 2022 World 
Championships are significantly different.  
\jy{elaborate on the inprepretation; what we have rejected;}

The p value from the two group comparison between the 2022 national
championships and World Championships was 0.000155. This value is for a one sided
test and the result is significant at $\alpha = 0.01$ and shows that
the times at the World Championships were significantly faster than at the
national championships.

>>>>

\begin{table}
  \centering
  \caption{Compares the various effect models by dataset, all probabilities are
  for observing a reaction time less than 0.1 seconds. In general the model with
  the highest probability (least extreme reaction time) is the Year Effect model.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & Year Effect & Batch Effect & Both Effects \\ 
   \midrule
   Old Pooled & $5.73\cdot10^{-3}$ & $5.21\cdot10^{-3}$ & $4.15\cdot10^{-3}$ \\ 
   All Pooled & $6.84\cdot10^{-3}$ & $6.64\cdot10^{-3}$ & $5.15\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:EffectComparison}
\end{table}

@@

\begin{table}
  \centering
  \caption{}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & $exact = True$ & $exact \neq True$ & Sample size & Clusters/Athletes \\ 
   \midrule
   2019 vs 2022 & $2.9\cdot10^{-3}$ & $2.3\cdot10{-2}$ & 65 & 15 \\ 
   Nat vs Inter & $2.2\cdot10^{-16}$ & $3.1\cdot10^{-4}$ & 61 & 15 \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}

Table~\ref{tab:Clusrankresults} shows the results generated from four tests in R.
We use a \texttt{clusWilcox.test()} and set the permutation number (B) to be
1000 as the sample size in this analysis is small.  The sample size indicates
the total number of observations while clusters represnts the number of athletes
in each dataset.  It is worth noting that it is entirely coincidental that there
are fiftenn athletes in sets.
